\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-26 exps.tex
updating citation

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{}, Robot and Access Environment Control
System (AECS) \cite{}. We have also added a set of customized hardware counters
to the original JOP design in order to collect numbers of clock cycles required
for logical ticks of given SystemJ program. All examples except Robot are
existing applications translated into pure SystemJ programs. The Robot example
models a combination of robotic arms and conveyors which splits goods based on
their volumetric sizes. Finally, garbage collector (GC) was disabled in all
experiments to avoid unwanted side-effects such as lengthening clock-domain
logical tick times. Whenever the GC triggers, experiment terminates. BCRT and
WCRT were then calculated based on data collected until that point.

>>>>

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{Bourke2009a}, Robot and Access Environment Control
System (AECS) \cite{aecs_ispa}. We have also added a set of customized hardware counters
to the original JOP design in order to collect numbers of clock cycles required
for logical ticks of given SystemJ program. All examples except Robot are
existing applications translated into pure SystemJ programs. The Robot example
models a combination of robotic arms and conveyors which splits goods based on
their volumetric sizes. Finally, garbage collector (GC) was disabled in all
experiments to avoid unwanted side-effects such as lengthening clock-domain
logical tick times. Whenever the GC triggers, experiment terminates. BCRT and
WCRT were then calculated based on data collected until that point.
